{{module}} Analysis

### 2024-03-18 templates/analysis-module-R/notebook-template.Rmd
remove rprojroot renv option

# The path to this module
module_base <- file.path(repository_base, "analyses", "{{module}}")
# If you are using `renv`, you might use something like the following instead:
# module_base <- rprojroot::find_root(rprojroot::is_renv_project)
```

>>>>

# The path to this module
module_base <- file.path(repository_base, "analyses", "{{module}}")
```
